Plant-pollintor networks worldwide are composed by the same specific building

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

Once we obtained $p_i^O$ and $p_i^E$, we used simulation to determine whether the former is likely to come from the latter or not, since the large number of possible motif combinations and the small probabilities for some of them advise against using an Exact test of goodness-of-fit or a Chi-square one. Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contains 10 million elements and, for each combination, the probability of being selected is equal to its expected probability. From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$. Following the usual interpretation for z-scores, motif combinations with $z_i^O > 1.96$ are over-represented, and those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level. Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).

>>>>

Once we obtained $p_i^O$ and $p_i^E$, we used simulation to determine whether the former is likely to come from the latter or not, since the large number of possible motif combinations and the small probabilities for some of them advise against using an Exact test of goodness-of-fit or a Chi-square one. Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability. From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$. Following the usual interpretation for z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level. Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
